A thesis draft

### 2018-11-11 res/sections/08-Background.tex
Fix english

In Figure~\ref{chap:background:img:openflow_protocol} it is possible to see the
how switches works in the OpenFlow protocol. Basically, OpenFlow swiches own a
set of tables to organizedpacket control and forwarding. These tables can be
updated by higher-level application, usually an SDN application or controller,
taking advatage of OpenFlow channels (OF channels).

\section{Virtualization}
Cloud computing is now leading-edge Internet technology and virtualization
technology is one of the important part of cloud computing system.
Virtualization, in computing, refers to the act of creating a virtual (rather
than actual) version of something, including but not limited to a virtual
computer hardware platform, operating system (OS), storage device, or computer
network resources. \todo{To change I do not what can I write, stolen from ``The
research and implementation of cloud computing platform based on docker'' paper}

\subsection{Network Virtualization}
%https://s3.amazonaws.com/academia.edu.documents/29016225/cs-2008-25.pdf?AWSAcce
%ssKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1541352965&Signature=On6XJ5daSAmnfJMnNf41f
%BNHFgg%3D&response-content-disposition=inline%3B%20filename%3DA_survey_of_netwo
%r k _virtualization.pdf
Virtualization, in the networking context, refers to the act of combining
hardware, software and functionalities into a virtual network. This abstraction
runs on the top of a physical network in a hypervisor, decupling the logical
network from the harwdare one. Network virtualization allow multiple,
heterogeneous networks to cohabit, increasing the flexibility and manageability.
%http://www.csc.villanova.edu/~nadi/csc8580/S11/DeeptiNune.pdf
%https://www.sciencedirect.com/science/article/abs/pii/S1389128609003387
The idea of network virtualization came from the decoupling of the role of the
traditional ISP into two different entities: who provides the infrastucture
(InPs) and who provides the services(SPs). In that context it is possible to
aggregate resources, even from different InPs, creating a virtual network,
offering an end-to-end service. Most known instances of NV are \emph{VPN},
dedicated networks that allows the communication among multiple sites, using
private and secure tunnels, relying on the public network such as Internet.
Other examples of netvork virtualization are \emph{overlay networks}. They are
logical networks, build on the top of an existing physical network, tipically
implemented at application layer.

\subsection{Network Function Virtualization}
The NFC concept refers to the use of virtualization tecnologies to virtualize
network nodes functions. VNFs may run different processes and softwares, on the
top of servers, switches, storage devices or on cloud computing infrastucture,
that substitute custom hardware. That approach worked well on the past, because
of the need to follow rigorous standards, providing at the same time high
quality, but it led to long product cycles and high specialized proprietary
hardware. New Internet senarios, that include IoT and the increasing number of
services to spread multimedia data (Skype, Netflix, Spotify, ...), requires
more flexibles function and faster network deployment. NFV technology is
exploited in a framework, composed at least by three components:
\begin{enumerate}
 \item a software that performs the network function that must be deployed,
 that is the VNF;
 \item NFV Infrastructure (NFVI) that are all hardware and software components
 that build the environment where VNFs are deployed;
 \item NFV Management And Orchestration (NFV-MANO) architectural framework that
 is all functional blocks, data repositories used by these blocks, and
 reference points and interfaces through which these functional blocks exchange
 information for the purpose of managing and orchestrating NFVI and VNFs.
\end{enumerate}

>>>>

In Figure~\ref{chap:background:img:openflow_protocol} it is possible to see the
how switches works in the OpenFlow protocol. Basically, OpenFlow swiches own a
set of tables to organized packet control and forwarding. These tables can be
updated by higher-level application, usually an SDN application or controller,
taking advatage of OpenFlow channels (called OF channels).

\section{Virtualization}
Cloud computing is now a leading-edge Internet technology and the virtualization
technology is one of the most important part of cloud computing systems.
Virtualization, in computing, refers to the act of creating a virtual (rather
than an actual) version of something, including but not limited to a virtual
computer hardware platform, operating system (OS), storage device, or computer
network resources. \todo{To change I do not what can I write, stolen from ``The
research and implementation of cloud computing platform based on docker'' paper}

\subsection{Network Virtualization}
%https://s3.amazonaws.com/academia.edu.documents/29016225/cs-2008-25.pdf?AWSAcce
%ssKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1541352965&Signature=On6XJ5daSAmnfJMnNf41f
%BNHFgg%3D&response-content-disposition=inline%3B%20filename%3DA_survey_of_netwo
%r k _virtualization.pdf
Virtualization, in the networking context, refers to the act of combining
hardware, software and functionalities into a virtual network. This abstraction
runs on the top of a physical network in a hypervisor, decupling the logical
network from the harwdare one. Network virtualization allow multiple,
heterogeneous networks to cohabit, increasing the flexibility and manageability.
%http://www.csc.villanova.edu/~nadi/csc8580/S11/DeeptiNune.pdf
%https://www.sciencedirect.com/science/article/abs/pii/S1389128609003387
The idea of network virtualization came from the decoupling of the role of the
traditional ISP into two different entities: who provides the infrastucture
(InPs) and who provides the services(SPs). In that context it is possible to
aggregate resources, even from different InPs, creating a virtual network,
offering an end-to-end service. Most known instances of NV are \emph{VPNs},
dedicated networks that allows the communication among multiple sites, using
private and secure tunnels, relying on the public network such as Internet.
Other examples of netvork virtualization are \emph{overlay networks}. They are
logical networks, build on the top of an existing physical network, tipically
implemented at the application layer.

\subsection{Network Function Virtualization}
The \emph{Network Function Virtualization} (NFV) concept refers to the use of 
virtualization tecnologies to virtualize network nodes functions. VNFs may run 
different processes and softwares, on the top of servers, switches, storage 
devices or on cloud computing infrastuctures, that substitute custom hardware. 
That approach worked well in the past, because of the need to follow rigorous 
standards, providing at the same time high quality, but it led to long product 
cycles and high specialized proprietary hardware. New Internet senarios, that 
include IoT and the increasing number of services to spread multimedia data 
(Skype, Netflix, Spotify, ...), requires more flexible functions and faster 
network deployments. The NFV technology is exploited in a framework, organized
at least by three components:
\begin{enumerate}
 \item a software that performs the network function that must be deployed,
 that is the VNF;
 \item NFV Infrastructure (NFVI) that is composed by all hardware and software 
components that builds the environment where the VNFs are deployed;
 \item NFV Management And Orchestration (NFV-MANO) architectural framework that
 is all the functional blocks, data repositories used by these blocks,
 reference points and interfaces through which these functional blocks exchange
 information for the purpose of managing and orchestrating NFVI and VNFs.
\end{enumerate}
